\sysfull

### 2019-10-01 paper/TOSN/intro.tex
space from footnote removed

\paragraph{Challenges and Contributions.}
We introduce \sys~\footnote{\sys's source code is accessible via \url{https://github.com/TUDSSL/Coala} }: a new task-based system that employs \emph{adaptive task size execution by task coalescing and splitting}. By means of this novel technique, small tasks can be executed efficiently by trimming unnecessary overhead \emph{dynamically}, meanwhile avoiding the risk of non-termination. \sys accepts any static decomposition and it coalesces (groups) tasks or splits them (see again Fig.~\ref{fig:coalesce}) based on the estimated energy availability without demanding any hardware support. To the best of our knowledge, \sys is the only system that eliminates restructuring and re-compilation of applications considering a device's energy buffer---enabling energy-storage independency for the applications, while keeping execution efficient.

>>>>

\paragraph{Challenges and Contributions.}
We introduce \sys\footnote{\sys's source code is accessible via \url{https://github.com/TUDSSL/Coala} }: a new task-based system that employs \emph{adaptive task size execution by task coalescing and splitting}. By means of this novel technique, small tasks can be executed efficiently by trimming unnecessary overhead \emph{dynamically}, meanwhile avoiding the risk of non-termination. \sys accepts any static decomposition and it coalesces (groups) tasks or splits them (see again Fig.~\ref{fig:coalesce}) based on the estimated energy availability without demanding any hardware support. To the best of our knowledge, \sys is the only system that eliminates restructuring and re-compilation of applications considering a device's energy buffer---enabling energy-storage independency for the applications, while keeping execution efficient.
